---
title: "NateVelarde_ChetGutwein_Lab1"
author: "Nate Velarde & Chet Gutwein"
date: "May 30, 2017"
output: pdf_document
---
```{r}
rm(list = ls())
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

## Introduction

\begin{center}
Is CEO salary related to company performance?
\end{center}

This section is reserved for Intro...
```{r}
getwd()
```
loading CEO object from workspace file...

```{r}
load("ceo_w203.RData")
objects()
```
loading standard EDA libraries...

```{r}
library(car)
library(dplyr)
library(Hmisc)
library(ggplot2)
str(CEO)
```


```{r}
summary(CEO)
head(CEO)
```
## Univariate Analysis

We will take a look at each variable 
```{r}
describe(CEO$salary)
hist(CEO$salary, breaks = c(-500, 500, 1500, 2500, 3500, 4500, 5500), main = "CEO Salary, 1990", 
     xlab = "Salary in $1,000")
boxplot(CEO$salary)
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
